The Rockerverse: Packages and Applications for Containerisation with R

### 2020-02-26 manuscript.Rmd
fix rendering

[CyVerse](https://cyverse.org) is an open source, NSF-funded cyberinfrastructure platform for the life sciences \citep{merchant2016iplant}.
CyVerse supports a browser-based 'data science workbench' called the [Discovery Environment (DE)](https://cyverse-de.github.io/), which uses a combination of [HTCondor](https://research.cs.wisc.edu/htcondor/) and Kubernetes for orchestrating container based analysis, it integrates with external HPC (High Performance Computing), NSF-XSEDE through [TAPIS] (https://www.tacc.utexas.edu/tapis) API's.
In addition, CyVerse provides a multi-petabyte Data Store based on [iRODS](https://irods.org/, this allows users to share and manage hundreds of GB's of data.
The DE uses an [OAuth](https://oauth.net/2/) system for single sign on (SSO) for its 70+ thousand registered users.
Rocker integration in the DE is designed to provide life science researchers with scalable, compute-intensive R analysis capabilities needed for large and complex datasets (e.g., genomics/multi-omics, GWAS, phenotypic data, spatial data etc.).
The DE runs Docker containers on demand, with users able to integrate containers from DockerHub or other registries \citep{devisetty2016bringing}.
These capabilities give users flexibility similar to Binder, but allows containers to run on larger computational resources (RAM, CPU, Disk), and for longer periods of time (days to weeks).
The Rocker Project's RStudio and Shiny containers are integrated into the DE by deriving new images from Rocker images.
These images include a reverse proxy using `nginx` to handle communication with CyVerse authentication systems.
All running instances are protected through this authentication system and users can invite other registered users to securely access the same instance \citep{rstudio_proxy_2020}.
Users can reference the same base image and add packages to further customize their R environment.
The Rocker base image is cached on all nodes in the Kubernetes environment to speed up launching.
CyVerse maintains its own [GitHub Organization](https://github.com/cyverse-vice/) with Dockerfiles and configuration scripts auto-built on DockerHub.
For additional reproducibility, CyVerse operates a private Docker image registry where a user's published, i.e., publicly available, containers are held.
CyVerse user accounts are free (with some limitations for non-US users) and the documentation repository [CyVerse Learning Center](https://learning.cyverse.org/) allows community members to document their containers to support training and education.

>>>>

[CyVerse](https://cyverse.org) is an open source, NSF-funded cyberinfrastructure platform for the life sciences \citep{merchant_iplant_2016}.
CyVerse supports a browser-based 'data science workbench' called the [Discovery Environment (DE)](https://cyverse-de.github.io/), which uses a combination of [HTCondor](https://research.cs.wisc.edu/htcondor/) and Kubernetes for orchestrating container based analysis, it integrates with external HPC (High Performance Computing), NSF-XSEDE through [TAPIS](https://www.tacc.utexas.edu/tapis) API's.
In addition, CyVerse provides a multi-petabyte Data Store based on [iRODS](https://irods.org/), this allows users to share and manage hundreds of GB's of data.
The DE uses an [OAuth](https://oauth.net/2/) system for single sign on (SSO) for its 70+ thousand registered users.
Rocker integration in the DE is designed to provide life science researchers with scalable, compute-intensive R analysis capabilities needed for large and complex datasets (e.g., genomics/multi-omics, GWAS, phenotypic data, spatial data etc.).
The DE runs Docker containers on demand, with users able to integrate containers from DockerHub or other registries \citep{devisetty_bringing_2016}.
These capabilities give users flexibility similar to Binder, but allows containers to run on larger computational resources (RAM, CPU, Disk), and for longer periods of time (days to weeks).
The Rocker Project's RStudio and Shiny containers are integrated into the DE by deriving new images from Rocker images.
These images include a reverse proxy using `nginx` to handle communication with CyVerse authentication systems.
All running instances are protected through this authentication system and users can invite other registered users to securely access the same instance \citep{rstudio_proxy_2020}.
Users can reference the same base image and add packages to further customize their R environment.
The Rocker base image is cached on all nodes in the Kubernetes environment to speed up launching.
CyVerse maintains its own [GitHub Organization](https://github.com/cyverse-vice/) with Dockerfiles and configuration scripts auto-built on DockerHub.
For additional reproducibility, CyVerse operates a private Docker image registry where a user's published, i.e., publicly available, containers are held.
CyVerse user accounts are free (with some limitations for non-US users) and the documentation repository [CyVerse Learning Center](https://learning.cyverse.org/) allows community members to document their containers to support training and education.
